%needs to be compiled with xelatex


\documentclass[]{deedy-resume-openfont}

\begin{document}

\lastupdated

\namesection{Joseph}{Corrado}{\urlstyle{same}\url{} \\
        \href{mailto:joseph.corrado@nyu.edu}{joseph.corrado@nyu.edu} |
        516-680-6221}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Education} 
\subsection{New York University}

\descript{BA in Physics}
\location{May 2019| New York, NY}
Secondary Major in Mathematics \\
College of Arts and Sciences\\
\location{Cum. GPA: 3.7 / 4.0 }
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/jcorrado76}{\custombold{jcorrado76}} \\
LinkedIn://  \href{https://www.linkedin.com/in/joseph-corrado-9737b2a6/}{\custombold{joseph-corrado-9737b2a6/}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Undergraduate}
Computational Particle Physics \\
(Research Asst.)\\
Quantum Mechanics\\
Electricity and Magnetism\\
Dynamics\\
Linear Algebra\\
Calculus\\
Probability and Statistics\\
Object Oriented Programming\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
Python (scientific stack) \textbullet{} Shell \textbullet{} C++ (ROOT framework) \textbullet{} Mathematica\\
LaTeX \textbullet{} VBA \\ 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{NYU Physics Department}
\descript{| Quarks to Cosmos Course Assistant }
\location{January 2018 –  May 2018 | New York, NY}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Assisted in the instruction of classes, as well as
        providing solutions manuals to homeworks, and support to the students.
\end{tightemize}
\sectionsep

\runsubsection{NYU Physics Department}
\descript{| General Physics I Tutor }
\location{September 2017 –  December 2017 | New York, NY}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}\item Tutored introductory physics to students in the college of arts
and sciences. 
\end{tightemize}
\sectionsep

\runsubsection{Courant Institute of Computational Sciences}\\
\descript{| Calculus and Linear Algebra Tutor}
\location{September 2016 – May 2017 | New York, NY}
\begin{tightemize}
\item Tutored Calculus I, II, III and Linear Algebra for the department. 
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research}
\runsubsection{NYU Experimental Particle Physics}
\descript{| Undergraduate Research Assistant}
\location{September 2016 – Present | New York, NY}
Worked with \textbf{\href{https://as.nyu.edu/content/nyu-as/as/faculty/allen-mincer.html}{Prof Allen Mincer}} 
to perform an analysis of the efficiency of algorithms used at the ATLAS
experiment at CERN. 
Determined thresholds needed to combine algorithms such that we get a higher
efficiency. \\
Contributed Algorithm Design to ATLAS Collaboration at the Large Hadron
Collider.
\sectionsep

\runsubsection{Center for Soft Matter}
\descript{| Undergraduate Research Assistant}
\location{May 2016– September 2016| New York, NY}
Studied random organization of particles in an immulsion when an external periodic shearing force is applied.
\textbf{\href{http://www.physics.nyu.edu/~pc86/people/chaikin.html}{Prof Paul Chaikin}} 
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
\begin{tabular}{rll}
2017	     & Fall NYU DURF  & Dean's Undergraduate Research Fund Recipient\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies} 

\begin{tabular}{rll}
2017 	& National    & Sigma Pi Sigma Physics Honor Society\\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
